---
title: "Communication Coding"
author: "Matt Blanchard"
date: "25/09/2019"
output: html_document
---

Need to decide whether to keep drivers with issues in the dataset


```{r setup, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

``` {r load, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
packages <- c("tidyverse", "corrr", "here", "knitr")
purrr::map(packages, library, character.only = TRUE)

# read sim variables
vars <- read_csv(here("data/200227_comms_efa_vars.csv")) %>% 
      filter(!team %in% c("17080712_1", "17080810_1"))  # remove outliers: collisions("17080810_1"), distance("17081510_2")

# read raw comms data
raw <- read_csv(here("data/200221_comms_raw.csv")) %>% 
  filter(team %in% vars$team) # remove outlier teams

# select which communication variables to analyse
comms_fac <- names(vars %>% select(inconsistent_codriver, terrible_codriver, helpful_exchange))
```

# Comparison of the mean number of communication events coded by each driver
``` {r echo=FALSE, message=FALSE, warning=FALSE}
raw %>% 
  group_by(team, Coder, event) %>% 
  summarise(n = n()) %>% 
  group_by(Coder, event) %>% 
  summarise(mean = mean(n)) %>% 
  filter(Coder != "All") %>% 
  ggplot(aes(x = Coder, y = mean, fill = Coder)) +
  geom_col() +
  facet_wrap(~event, scales = "free_y")

# number of videos completed by each coder
x <- raw %>% select(team, Coder) %>% unique() %>% group_by(Coder) %>% count()

kable(x)

```

# Descriptives and distributions for communication variables overall
``` {r echo=FALSE, message=FALSE, warning=FALSE}
x <- vars %>% 
  select(team:sit.awareness_driver) %>% 
  select(-contains("ratio")) %>% 
         # collisions_overall_improve:collisions_max_recovery) %>% 
  gather(var, val, -team) %>% 
  group_by(var) %>% 
  summarise(mean = mean(val, na.rm = T),
            sd = sd(val, na.rm = T))

kable(x)

vars %>% 
  select(team:sit.awareness_driver) %>% 
  select(-contains("ratio")) %>%  
         # collisions_overall_improve:collisions_max_recovery) %>% 
  gather(var, val, -team) %>% 
  ggplot(aes(x = val)) +
  geom_histogram() +
  facet_wrap(~var, scales = "free") +
  theme_minimal()
```

# Reliability for each communication variable overall
``` {r echo=FALSE, message=FALSE, warning=FALSE}
# reliability for each comms variable
name <- names(vars %>% select(co_info_help_overall:co_ratio_overall, -contains("ratio")))
              
name <- gsub("_overall", "", name)

lapply(name, function(i) {
  x <- vars %>%
    ungroup() %>% 
    select(team, co_info_harm_1:drive_total_5) %>% 
    gather(var, val, -team) %>% 
    mutate(lap = str_extract(var, "_[1-5]"),
           lap = as.numeric(str_remove(lap, "_")),
           var = str_remove(var, "_[1-5]")) %>% 
    filter(var == i) %>% 
    spread(lap, val) %>% 
    select(-team, -var)
  
  paste0(i, " = ", round(psych::alpha(x)$total$raw_alpha, 2))
})
```

<!-- # Descriptives and distributions for communication variables for fog/no fog -->
<!-- ``` {r echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- x <- vars %>%  -->
<!--   select(team, co_info_harm_fog:drive_total_no_fog) %>%  -->
<!--   select(-contains("ratio")) %>%  -->
<!--   gather(var, val, -team) %>%  -->
<!--   mutate(e = ifelse(str_detect(var, "no_fog"), "no_fog", "fog"), -->
<!--          var = str_remove(var, "_no_fog"), -->
<!--          var = str_remove(var, "_fog")) %>%  -->
<!--   group_by(e, var) %>%  -->
<!--   summarise(mean = mean(val, na.rm = T), -->
<!--             sd = sd(val, na.rm = T)) %>%  -->
<!--   gather(var2, val, mean, sd) %>%  -->
<!--   unite(var2, var2, e) %>%  -->
<!--   spread(var2, val) -->

<!-- kable(x) -->

<!-- vars %>%  -->
<!--   select(team, co_info_harm_fog:drive_total_no_fog) %>%  -->
<!--   select(-contains("ratio")) %>%   -->
<!--   gather(var, val, -team) %>%  -->
<!--   ggplot(aes(x = val)) + -->
<!--   geom_histogram() + -->
<!--   facet_wrap(~var, scales = "free") + -->
<!--   theme_minimal() -->
<!-- ``` -->

<!-- # Reliability for each communication variable fog/no fog -->
<!-- ``` {r echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- # reliability for each comms variable -->
<!-- name <- names(vars %>% select(co_info_harm_fog:drive_total_no_fog, -contains("ratio"))) -->

<!-- lapply(name, function(i) { -->
<!--   x <- vars %>% -->
<!--     ungroup() %>%  -->
<!--     select(team, co_info_harm_fog_1:drive_total_no_fog_5) %>%  -->
<!--     gather(var, val, -team) %>%  -->
<!--     mutate(lap = str_extract(var, "_[1-5]"), -->
<!--            lap = as.numeric(str_remove(lap, "_")), -->
<!--            var = str_remove(var, "_[1-5]")) %>%  -->
<!--     filter(var == i) %>%  -->
<!--     spread(lap, val) %>%  -->
<!--     select(-team, -var) -->

<!--   paste0(i, " = ", round(psych::alpha(x)$total$raw_alpha, 2)) -->
<!-- }) -->
<!-- ``` -->

# Relationships between communication variables and time_talking variables overall
Validation check: do the communication coding varaibles relate to the time talking variables
``` {r echo=FALSE, message=FALSE, warning=FALSE}
x <- vars %>%
  select(co_total_overall, drive_total_overall, time_talking_overall, time_talking_events_overall, 
         time_talking_none_overall, time_talking_overall_drone, time_talking_events_overall_drone,
         time_talking_none_overall_drone) %>% 
  correlate() %>% focus(drive_total_overall, co_total_overall)

col_names <- x %>% select(rowname)

x <- round(x[,-1],2) %>% 
  bind_cols(col_names) %>% 
  select(rowname, drive_total_overall, co_total_overall)

x[x < .270] <- NA

kable(x)

```

# Relationship between communication variables and time_talking variables per lap
``` {r echo=FALSE, message=FALSE, warning=FALSE}
x <- vars %>%
  select(co_total_1:co_total_5, drive_total_1:drive_total_5, 
         time_talking_1:time_talking_5, time_talking_events_1:time_talking_events_5, 
         time_talking_none_1:time_talking_none_5, 
         time_talking_1_drone:time_talking_5_drone, 
         time_talking_events_1_drone:time_talking_events_5_drone,
         time_talking_none_1_drone:time_talking_none_5_drone) %>% 
  correlate() %>% focus(co_total_1:co_total_5, drive_total_1:drive_total_5)

col_names <- x %>% select(rowname)

x <- round(x[,-1],2) %>% 
  bind_cols(col_names) %>% 
  select(rowname, co_total_1:drive_total_5)

x[x < .270] <- NA

kable(x)

```

# Relationships between communication variables
Is there a multicollinearity issue?
All correlations below .5 are suppressed
``` {r echo=FALSE, message=FALSE, warning=FALSE}
x <- vars %>%
  select(co_info_help_overall:sit.awareness_driver, -contains("ratio")) %>% 
  correlate()

x[x < .5] <- NA

kable(x)

```

It looks like there is a multicollinearity issue. Need to reduce comms variables to a smaller number using factor analysis.

# Conduct EFA to extract comms factors
Reduce variables to smaller number of factors and correlate with each other. It looks like 3 components can be extracted from the comms variables.

## Correlations between original comms variables
``` {r echo=FALSE, message=FALSE, warning=FALSE}
library(corrplot)

# select original comms variables
pca <- vars %>% dplyr::select(co_info_help_overall:drive_frust_overall, 
                -contains("ratio"), -co_total_help_overall, 
                -co_total_harm_overall, -co_total_overall)

# create the correlation matrix for PCA so we know how it was done (e.g., how missing values were treated)
cor_pca <- cor(pca, use="pairwise.complete.obs")

# print correlations
kable(round(cor_pca, 2))

# Visualise correlations to see if variables appear to cluster
corrplot(cor(pca, use="complete.obs"), order = "hclust", tl.col='black', tl.cex=.75)

```

## KMO and Bartlett's test of Spherecity
``` {r echo=FALSE, message=FALSE, warning=FALSE}
library(psych)

# Kaiser-Meyer-Olkin Measure of Sampling Adequacy (KMO)
print(KMO(cor_pca))

# Bartlett's test of spherecity
print("Bartletts test of spherecity")
print(data.frame(cortest.bartlett(cor_pca, n = 55)))
```

## Communalities
``` {r echo=FALSE, message=FALSE, warning=FALSE}
library(GPArotation)

# 3-component PCA
n_comp <- 3
rotate_method <- "promax"
score_method <- "Bartlett"

fit <- principal(pca, rotate = rotate_method, nfactors = n_comp, 
                        method = score_method, scores = TRUE, n.obs = 55)

# communalities
x <- data.frame(communalities = fit$communality)

kable(x)

```

## Variance explained by the extracted components
``` {r echo=FALSE, message=FALSE, warning=FALSE}
# variance explained
x <- data.frame(component = 1:9,
           eigen = fit$values,
           prop_var = c(fit$Vaccounted[2,c(1:3)], rnorm(6, 0, 0)),
           cum_var = c(fit$Vaccounted[3,c(1:3)], rnorm(6, 0, 0)),
           rotation_SS_load = c(fit$Vaccounted[1,c(1:3)], rnorm(6, 0, 0))) %>% 
  round(2)

x[x == 0] <- ""

kable(x)

# Scree plot
p <- data.frame(component = 1:9,
           eigen = fit$values)

p %>% ggplot(aes(x = component, y = eigen)) +
  geom_line() + geom_point() +
  scale_x_continuous(breaks = 1:9) +
  theme_minimal() +
  labs(title = "Scree plot") +
  theme(plot.title = element_text(hjust = 0.5))

```

## Pattern matrix
``` {r echo=FALSE, message=FALSE, warning=FALSE}
# pattern matrix
load <- data.frame(var = rownames(fit$loadings),
                   PC1 = round(fit$loadings[1:9], 2),
                   PC2 = round(fit$loadings[10:18], 2),
                   PC3 = round(fit$loadings[19:27], 2)) %>% 
  mutate(PC1 = ifelse(PC1 < .3 & PC1 > -.3, "", PC1),
         PC2 = ifelse(PC2 < .3 & PC2 > -.3, "", PC2),
         PC3 = ifelse(PC3 < .3 & PC3 > -.3, "", PC3)) %>% 
  arrange(desc(PC1), desc(PC2), desc(PC3))
  
kable(load)

```

## Component correlations matrix
``` {r echo=FALSE, message=FALSE, warning=FALSE}
# Component correlations matrix
rownames(fit$r.scores) <- c("inconsistent", "terrible", "helpful")
colnames(fit$r.scores) <- c("inconsistent", "terrible", "helpful")

round(fit$r.scores,2)

```

## Check that component scores extracted using SPSS and R are the same
``` {r echo=FALSE, message=FALSE, warning=FALSE}
# save component scores as dataframe
pca_scores <- data.frame(fit$scores) %>% 
  rename(inconsistent_codriver_r = RC1, terrible_codriver_r = RC2, helpful_exchange_r = RC3)

# append component scores to dataset
vars <- cbind(vars, pca_scores)

# check that spss and r component scores are the same
cor1 <- cor.test(vars$inconsistent_codriver, vars$inconsistent_codriver_r)
cor2 <- cor.test(vars$terrible_codriver, vars$terrible_codriver_r)
cor3 <- cor.test(vars$helpful_exchange, vars$helpful_exchange_r)

data.frame(component = c("inconsistent_codriver", "terrible_codriver", "helpful_exchange"),
           r = round(c(cor1$estimate, cor2$estimate, cor3$estimate),4))

```

# Descriptives statistics
## Driver
``` {r echo=FALSE, message=FALSE, warning=FALSE}
x <- vars %>% 
  select(team, driving_years:neuroticism) %>% 
  gather(var, val, -team) %>% 
  mutate(var = str_remove(var, "_drone")) %>% 
  group_by(var) %>% 
  summarise(mean = mean(val, na.rm = T),
            sd = sd(val, na.rm = T))

kable(x)
```

## Drone
``` {r echo=FALSE, message=FALSE, warning=FALSE}
x <- vars %>% 
  select(team, driving_years_drone:neuroticism_drone) %>% 
  gather(var, val, -team) %>% 
  mutate(var = str_remove(var, "_drone")) %>% 
  group_by(var) %>% 
  summarise(mean = mean(val, na.rm = T),
            sd = sd(val, na.rm = T))

kable(x)
```

# Driver: relationship between communication factors and psych variables
``` {r echo=FALSE, message=FALSE, warning=FALSE}
x <- vars %>% 
  select(comms_fac, leadership:teamwork, leadership_driver, sit.awareness_driver, age_driver, sex_driver, mean_age, prop_female, driving_years:neuroticism) %>% 
  select(-contains("ratio")) %>% 
  correlate() %>% focus(age_driver:neuroticism)

col_names <- x %>% select(rowname)

x <- round(x[,-1],2) %>% 
  bind_cols(col_names) %>% 
  select(rowname, age_driver:neuroticism)

x[x < .270] <- NA

kable(x)

```

<!-- # Driver: relationship between fog/no fog communication variables and psych variables -->
<!-- ``` {r echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- x <- vars %>%  -->
<!--   select(drive_frust_fog:drive_total_no_fog, age_driver, sex_driver,  -->
<!--          mean_age, prop_female, driving_years:neuroticism) %>%  -->
<!--   select(-contains("ratio")) %>%  -->
<!--   correlate() %>% focus(age_driver:neuroticism) -->

<!-- col_names <- x %>% select(rowname) -->

<!-- x <- round(x[,-1],2) %>%  -->
<!--   bind_cols(col_names) %>%  -->
<!--   select(rowname, age_driver:neuroticism) -->

<!-- x[x < .270] <- NA -->

<!-- kable(x) -->
<!-- ``` -->

# Driver: relationship between communication variables and NASA-TLX (self)
The more the driver and drone operator communicated the more effortful and demanding the driver found the task. Interestingly, for the driver there is no relationship between the quantity or type of communication and their subjective assessment of their own performance.
``` {r echo=FALSE, message=FALSE, warning=FALSE}
x <- vars %>% 
  select(comms_fac, leadership:teamwork, leadership_driver, sit.awareness_driver, effort:temporal_demand, -contains("ratio")) %>% 
  correlate() %>% focus(effort:temporal_demand)
  
col_names <- x %>% select(rowname)

x <- round(x[,-1],2) %>% 
  bind_cols(col_names) %>% 
  select(rowname, effort:temporal_demand)

x[x < .270 & x > -.270] <- NA

kable(x)
```

# Driver: relationship between communication variables and NASA-TLX (other)
The more the driver and drone operator communicated the more effortful and demanding the driver thought the task was for the drone operator. The higher the frequency of helpful communication (info and instruct) and total communication, and the more questions the drone operator asked the higher the driver's subjective assessment of the drone operator's performance.
``` {r echo=FALSE, message=FALSE, warning=FALSE}
x <- vars %>% 
  select(comms_fac, leadership:teamwork, leadership_driver, sit.awareness_driver,
         effort_other:temporal_demand_other, -contains("ratio")) %>% 
  correlate() %>% focus(effort_other:temporal_demand_other)

col_names <- x %>% select(rowname)

x <- round(x[,-1],2) %>% 
  bind_cols(col_names) %>% 
  select(rowname, effort_other:temporal_demand_other)

x[x < .270 & x > -.270] <- NA

kable(x)
```

# Drone: relationship between overall communication variables and psych variables
``` {r echo=FALSE, message=FALSE, warning=FALSE}
x <- vars %>% 
  select(comms_fac, leadership:teamwork, leadership_co_driver, sit.awareness_co_driver, age_co_driver, sex_co_driver, mean_age, prop_female, 
         driving_years_drone:neuroticism_drone) %>% 
  select(-contains("ratio")) %>% 
  correlate() %>% focus(age_co_driver:neuroticism_drone)

col_names <- x %>% select(rowname)

x <- round(x[,-1],2) %>% 
  bind_cols(col_names) %>% 
  select(rowname, age_co_driver:neuroticism_drone)

x[x < .270 & x > -.270] <- NA

kable(x)
```

<!-- # Drone: relationship between fog/no fog communication variables and psych variables -->
<!-- ``` {r echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- x <- vars %>%  -->
<!--   select(co_info_harm_fog:co_total_no_fog, age_co_driver, sex_co_driver, mean_age,  -->
<!--        prop_female, driving_years_drone:neuroticism_drone) %>%  -->
<!--   select(-contains("ratio")) %>%  -->
<!--   correlate() %>% focus(age_co_driver:neuroticism_drone) -->

<!-- col_names <- x %>% select(rowname) -->

<!-- x <- round(x[,-1],2) %>%  -->
<!--   bind_cols(col_names) %>%  -->
<!--   select(rowname, age_co_driver:neuroticism_drone) -->

<!-- x[x < .270] <- NA -->

<!-- kable(x) -->
<!-- ``` -->

# Drone: relationship between communication variables and NASA-TLX (self)
``` {r echo=FALSE, message=FALSE, warning=FALSE}
x <- vars %>% 
  select(comms_fac, leadership:sit.awareness_driver,
         effort_drone:temporal_demand_drone) %>% 
  select(-contains("ratio")) %>% 
  correlate() %>% focus(effort_drone:temporal_demand_drone)

col_names <- x %>% select(rowname)

x <- round(x[,-1],2) %>% 
  bind_cols(col_names) %>% 
  select(rowname, effort_drone:temporal_demand_drone)

x[x < .270 & x > -.270] <- NA

kable(x)
```

# Drone: relationship between communication variables and NASA-TLX (other)
``` {r echo=FALSE, message=FALSE, warning=FALSE}
x <- vars %>% 
    select(comms_fac, leadership:sit.awareness_driver, effort_other_drone:temporal_demand_other_drone) %>%
    select(-contains("ratio")) %>% 
  correlate() %>% focus(effort_other_drone:temporal_demand_other_drone)

col_names <- x %>% select(rowname)

x <- round(x[,-1],2) %>% 
  bind_cols(col_names) %>% 
  select(rowname, effort_other_drone:temporal_demand_other_drone)

x[x < .270 & x > -.270] <- NA

kable(x)
```

# Relationship between communication variables and simulation-derived metrics
## Descriptives for simulation-derived metrics
``` {r echo=FALSE, message=FALSE, warning=FALSE}
x <- vars %>%
  ungroup() %>% 
  select(team, collisions_1:collisions_5, speed_1:speed_5, 
         distance_1_deviation:distance_5_deviation) %>% 
  gather(var, val, -team) %>% 
  mutate(lap = str_extract(var, "_[1-5]"),
         lap = as.numeric(str_remove(lap, "_")),
         var = str_remove(var, "_[1-5]")) %>% 
  group_by(var, lap) %>% 
  summarise(mean = mean(val),
            sd = sd(val))

kable(x)

x <- vars %>%
  ungroup() %>% 
  select(team, collisions_1:collisions_5, speed_1:speed_5, 
         distance_1_deviation:distance_5_deviation) %>% 
  gather(var, val, -team) %>% 
  mutate(lap = str_extract(var, "_[1-5]"),
         lap = as.numeric(str_remove(lap, "_")),
         var = str_remove(var, "_[1-5]")) %>% 
  group_by(var) %>% 
  summarise(mean = mean(val),
            sd = sd(val))

kable(x)
```

## Reliability estimates for simulation-derived metrics
## Overall
``` {r echo=FALSE, message=FALSE, warning=FALSE}
# reliability for each simulation-derived metrics
name <- c("collisions", "distance", "speed")

lapply(name, function(i) {
  x <- vars %>%
    ungroup() %>% 
    select(team, collisions_1:collisions_5, speed_1:speed_5, 
           distance_1:distance_5) %>% 
    gather(var, val, -team) %>% 
    mutate(lap = str_extract(var, "_[1-5]"),
           lap = as.numeric(str_remove(lap, "_")),
           var = str_remove(var, "_[1-5]")) %>% 
    filter(var == i) %>% 
    spread(lap, val) %>% 
    select(-team, -var)
  
  paste0(i, " = ", round(psych::alpha(x)$total$raw_alpha, 2))
})

```

## Fog free periods
``` {r echo=FALSE, message=FALSE, warning=FALSE}
# reliability for each simulation-derived metrics
name <- c("collisions_no_fog", "speed_no_fog", "distance_no_fog")

lapply(name, function(i) {
  x <- vars %>%
    ungroup() %>% 
    select(team, collisions_no_fog_1:collisions_no_fog_5, speed_no_fog_1:speed_no_fog_5, 
           distance_no_fog_1:distance_no_fog_5) %>% 
    gather(var, val, -team) %>% 
    mutate(lap = str_extract(var, "_[1-5]"),
           lap = as.numeric(str_remove(lap, "_")),
           var = str_remove(var, "_[1-5]")) %>% 
    filter(var == i) %>% 
    spread(lap, val) %>% 
    select(-team, -var)

  paste0(i, " = ", round(psych::alpha(x)$total$raw_alpha, 2))
})

```

## Fog-event probe
``` {r echo=FALSE, message=FALSE, warning=FALSE}
# reliability for each simulation-derived metrics
name <- c("collisions_fog", "speed_fog", "distance_fog")

lapply(name, function(i) {
  x <- vars %>%
    ungroup() %>% 
    select(team, collisions_fog_1:collisions_fog_5, speed_fog_1:speed_fog_5, 
           distance_fog_1:distance_fog_5) %>% 
    gather(var, val, -team) %>% 
    mutate(lap = str_extract(var, "_[1-5]"),
           lap = as.numeric(str_remove(lap, "_")),
           var = str_remove(var, "_[1-5]")) %>% 
    filter(var == i) %>% 
    spread(lap, val) %>% 
    select(-team, -var)

  paste0(i, " = ", round(psych::alpha(x)$total$raw_alpha, 2))
})

```

## Distributions for simulation-derived metrics
``` {r echo=FALSE, message=FALSE, warning=FALSE}
library(cowplot)

# collisions plot
c <- vars %>% 
  ggplot(aes(x=collisions_overall)) +
  geom_histogram(colour = "black", fill = "white", binwidth = 40) +
  labs(x = "Collisions", y = "Frequency") +
  scale_x_continuous(breaks = seq(0,650, 200), limits = c(1,650)) +
  scale_y_continuous(breaks=seq(0,14,2), limits = c(0,14)) +
  theme(panel.background = element_blank())

# speed plot
s <- vars %>% 
  ggplot(aes(x = speed_overall)) +
  geom_histogram(colour = "black", fill = "white", binwidth = .5) +
  labs(x = "Speed", y = "") +
  scale_x_continuous(breaks = seq(4,12,2), limits = c(4,12)) +
  scale_y_continuous(breaks=seq(0,9,2), limits = c(0,9)) +
  theme(panel.background = element_blank())

# distance deviation plot
d <- vars %>% 
  ggplot(aes(x = distance_overall_deviation)) +
  geom_histogram(colour = "black", fill = "white", binwidth = 400) +
  labs(x = "Distance deviation", y = "Frequency") +
  scale_x_continuous(breaks = seq(-2000,6000,2000), limits = c(-2000,6000)) +
  scale_y_continuous(breaks=seq(0,14,2), limits = c(0,14)) +
  theme(panel.background = element_blank())

# combine plots into single figure
plot_grid(c, s, d, labels = c("A", "B", "C"))

# save as lossless png file
# ggsave("output/sim_metric_distributions.png")
```



## Collisions overall
``` {r echo=FALSE, message=FALSE, warning=FALSE}
x <- vars %>% 
  select(comms_fac, leadership:sit.awareness_driver,
         age_co_driver:prop_female, 
         collisions_overall) %>% 
        select(-contains("ratio")) %>% 
  correlate() %>% focus(collisions_overall)

col_names <- x %>% select(rowname)

x <- round(x[,-1],2) %>% 
  bind_cols(col_names) %>% 
  select(rowname, contains("collisions"), contains("speed"))

x[x < .270 & x > -.270] <- NA

kable(x)
```

## Collisions per lap overall
``` {r echo=FALSE, message=FALSE, warning=FALSE}
x <- vars %>% 
  select(collisions_1:collisions_5,
         co_info_harm_1:drive_total_5) %>% 
         select(-contains("ratio")) %>% 
  correlate() %>% focus(collisions_1:collisions_5)

col_names <- x %>% select(rowname)

x <- round(x[,-1],2) %>% 
  bind_cols(col_names) %>% 
  select(rowname, contains("collisions"), contains("speed"))

x[x < .270 & x > -.270] <- NA

kable(x)
```

<!-- ## Collisions fog/no fog -->
<!-- ``` {r echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- x <- vars %>%  -->
<!--   select(co_info_harm_fog:drive_total_no_fog, age_co_driver:prop_female, collisions_fog_overall, collisions_no_fog_overall) %>%  -->
<!--   select(-contains("ratio")) %>%  -->
<!--   correlate() %>% focus(collisions_fog_overall, collisions_no_fog_overall) %>%  -->
<!--   arrange(str_detect(rowname, "fog"), str_detect(rowname, "no_fog")) -->

<!-- col_names <- x %>% select(rowname) -->

<!-- x <- round(x[,-1],2) %>%  -->
<!--   bind_cols(col_names) %>%  -->
<!--   select(rowname, contains("collisions"), contains("speed")) -->

<!-- x[x < .270] <- NA -->

<!-- kable(x) -->
<!-- ``` -->

<!-- ## Collisions per lap fog/no fog -->
<!-- ``` {r echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- x <- vars %>%  -->
<!--   select(collisions_fog_1:collisions_fog_5, collisions_no_fog_1:collisions_no_fog_5, -->
<!--          co_info_harm_fog_1:drive_total_no_fog_5) %>%  -->
<!--          select(-contains("ratio")) %>%  -->
<!--   correlate() %>% focus(collisions_fog_1:collisions_fog_5, collisions_no_fog_1:collisions_no_fog_5) %>%  -->
<!--   arrange(str_detect(rowname, "fog"), str_detect(rowname, "no_fog")) -->

<!-- col_names <- x %>% select(rowname) -->

<!-- x <- round(x[,-1],2) %>%  -->
<!--   bind_cols(col_names) %>%  -->
<!--   select(rowname, contains("collisions"), contains("speed")) -->

<!-- x[x < .270] <- NA -->

<!-- kable(x) -->
<!-- ``` -->


## Speed overall
``` {r echo=FALSE, message=FALSE, warning=FALSE}
x <- vars %>% 
  select(comms_fac, leadership:sit.awareness_driver, 
         age_co_driver:prop_female, speed_overall) %>% 
  select(-contains("ratio")) %>% 
  correlate() %>% focus(speed_overall)

col_names <- x %>% select(rowname)

x <- round(x[,-1],2) %>% 
  bind_cols(col_names) %>% 
  select(rowname, contains("collisions"), contains("speed"))

x[x < .270 & x > -.270] <- NA

kable(x)
```

## Speed per lap overall
``` {r echo=FALSE, message=FALSE, warning=FALSE}
x <- vars %>% 
  select(speed_1:speed_5, 
         co_info_harm_1:drive_total_5) %>% 
  select(-contains("ratio")) %>% 
  correlate() %>% focus(speed_1:speed_5)

col_names <- x %>% select(rowname)

x <- round(x[,-1],2) %>% 
  bind_cols(col_names) %>% 
  select(rowname, contains("collisions"), contains("speed"))

x[x < .270 & x > -.270] <- NA

kable(x)
```


<!-- ## Speed fog/no fog overall -->
<!-- ``` {r echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- x <- vars %>%  -->
<!--   select(co_info_harm_fog:drive_total_no_fog, age_co_driver:prop_female, speed_fog_overall, speed_no_fog_overall) %>%  -->
<!--         select(-contains("ratio")) %>%  -->
<!--   correlate() %>% focus(speed_fog_overall, speed_no_fog_overall) %>%  -->
<!--   arrange(str_detect(rowname, "fog"), str_detect(rowname, "no_fog")) -->

<!-- col_names <- x %>% select(rowname) -->

<!-- x <- round(x[,-1],2) %>%  -->
<!--   bind_cols(col_names) %>%  -->
<!--   select(rowname, contains("collisions"), contains("speed")) -->

<!-- x[x < .270] <- NA -->

<!-- kable(x) -->
<!-- ``` -->

<!-- ## Speed per lap fog/no fog -->
<!-- ``` {r echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- x <- vars %>%  -->
<!--   select(speed_fog_1:speed_fog_5, speed_no_fog_1:speed_no_fog_5, -->
<!--          co_info_harm_fog_1:drive_total_no_fog_5) %>%  -->
<!--          select(-contains("ratio")) %>%  -->
<!--   correlate() %>% focus(speed_fog_1:speed_fog_5, speed_no_fog_1:speed_no_fog_5) -->

<!-- col_names <- x %>% select(rowname) -->

<!-- x <- round(x[,-1],2) %>%  -->
<!--   bind_cols(col_names) %>%  -->
<!--   select(rowname, contains("collisions"), contains("speed")) -->

<!-- x[x < .270 & x > -.270] <- NA -->

<!-- kable(x) -->
<!-- ``` -->

# Distance deviation
``` {r echo=FALSE, message=FALSE, warning=FALSE}
x <- vars %>% 
    select(comms_fac, leadership:sit.awareness_driver, age_co_driver:prop_female, distance_overall_deviation) %>%
  select(-contains("ratio")) %>% 
  correlate() %>% focus(distance_overall_deviation)

col_names <- x %>% select(rowname)

x <- round(x[,-1],2) %>% 
  bind_cols(col_names) %>% 
  select(rowname, contains("deviation"))

x[x < .270 & x > -.270] <- NA

kable(x)
```

## Distance deviation per lap overall
``` {r echo=FALSE, message=FALSE, warning=FALSE}
x <- vars %>% 
  select(distance_1_deviation:distance_5_deviation, 
         co_info_harm_1:drive_total_5) %>% 
  select(-contains("ratio")) %>% 
  correlate() %>% focus(distance_1_deviation:distance_5_deviation)

col_names <- x %>% select(rowname)

x <- round(x[,-1],2) %>% 
  bind_cols(col_names) %>% 
  select(rowname, contains("collisions"), contains("distance"))

x[x < .270 & x > -.270] <- NA

kable(x)
```

# Regression 
## Sig. correaltions between simulation-derived metrics and comms and psych variables overall
``` {r echo=FALSE, message=FALSE, warning=FALSE}
x <- vars %>% 
  select(comms_fac, leadership:sit.awareness_driver,
    driving_years:neuroticism, effort:temporal_demand, driving_years_drone:neuroticism_drone, effort_drone:temporal_demand_drone, age_co_driver:prop_female,
                -contains("ratio"),
                collisions_overall, speed_overall, distance_overall_deviation) %>% 
  correlate() %>% focus(collisions_overall, speed_overall, distance_overall_deviation) %>% 
  gather(var, val, -rowname) %>% 
  mutate(val = round(val, 2)) %>% 
  spread(var, val)

x[x > -.270 & x < .270] <- NA

name <- names(x)[-1]

map(name, function(i) {
  x <- x %>% select(rowname, i) %>% na.omit()
  kable(x)
})
```

## Regression overall
``` {r echo=FALSE, message=FALSE, warning=FALSE}
# functions to fit regression models and check assumptions + multicollinearity
library(car) # load package to diagnose multicollinearity
library(GGally)
library(olsrr)
library(mctest)

select_vars <- function(dv_index) {
  a <- na.omit(x[c(1, dv_index)]) %>% select(rowname) %>% 
    filter(!rowname %in% c("sex_driver", "sex_co_driver", "sit.awareness_driver", 
                           "sit.awareness_co_driver", "sit.awareness",
                           "leadership_driver", "leadership_co_driver", "leadership"))
  
  vars %>% select(a$rowname)
}

# function to select IVs, fit regression model, and run diagnostics for overall simulation-derived metrics
regress <- function(dv) {
  # print dv name
  print(paste0("DV = ", dv))
  n <- names(var)
  
  var_std <- var %>% 
    # mutate(prop_female = factor(prop_female)) %>% 
    mutate_if(is.numeric, scale, center=TRUE, scale=TRUE)
  
  print(psych::describe(var_std))
  
  # create regression formula
  fm <- as.formula(paste0("vars$", dv, " ~ ", paste(n, collapse = " + ")))
  
  # fit model
  f <- lm(fm, data = var)
  
  # results
  print(summary(f))
  
  print(ols_correlations(f))
   
  # check assumptions and multicollinearity
  plot(f)
  
  # plot correlations between IVs
  p <- vars %>% select(n) %>% 
    ggcorr(method = "pairwise.complete.obs", 
           label = TRUE, label_size = 3, label_round = 2, label_alpha = TRUE, # add text correlations value to plot
           hjust = 0.9, size = 4, color = "grey50", layout.exp = 3) # move variable labels
  # more detailed plot: distribution, scatterplot, correlations
  # vars %>% select(x, issue) %>% 
  #   ggpairs(., lower = list(continuous = wrap("smooth", alpha = 0.3, size=0.1)))
  
  # print correlation plot
  print(p)

  # check for multicollinearity
  print(mctest::omcdiag(f))
  
  print(mctest::imcdiag(f))
   
}



# function to select IVs, fit regression model, and run diagnostics for event simulation-derived metrics (no fog/fog)
fog_regress <- function(dv) {
  # select variables
  a <- na.omit(x %>% select(rowname, dv)) %>% 
    # select(rowname) %>% 
    filter(!rowname %in% c("sit.awareness_driver", "sit.awareness_co_driver", "sit.awareness",
                           "leadership_driver", "leadership_co_driver", "leadership"))
  
  a <- a %>% filter(!rowname %in% c("sex_driver", "sex_co_driver"))
  
  var <- vars %>% select(dv, a$rowname)
  name <- names(var[-1])
  # create regression formula
  fm <-   as.formula(paste(dv, " ~ ", paste(name, collapse = " + ")))
  
  
  
  # fit model
  f <- lm(fm, data = var)
  
  # print dv name
  print(dv)
  
  # results
  summary(f)
  
  # })
}

# function for adding interactions to regression iteratively
# names of comms factors
interact_female <- function(dv) {
  map(comms_fac, function(i) {
    if (all(c(i, "prop_female") %in% names(var))) {
      # standardise IVs
      var_std <- var %>% 
      # mutate(prop_female = factor(prop_female)) %>% 
      mutate_if(is.numeric, scale, center=TRUE, scale=TRUE)
  
      fm <- as.formula(paste0("vars$", dv, "~", paste0(i, "*prop_female", " + .")))
      
      f <- lm(fm, data = var_std)
      
      summary(f)
    }
  })
}


interact_sex <- function(a) {
  map(comms_fac, function(i) {
    if (all(c(i, "sex_driver") %in% names(var))) {
      # standardise IVs
      var_std <- var %>% 
      # mutate(prop_female = factor(prop_female)) %>% 
      mutate_if(is.numeric, scale, center=TRUE, scale=TRUE)
  
      print(psych::describe(var_std))
  
      fm <- as.formula(paste0("vars$", a, "~", paste0(i, "*sex_driver", " + .")))
      
      f <- lm(fm, data = var_std)
      
      summary(f)
    }
  })
}

```

## Collisions overall
``` {r echo=FALSE, message=FALSE, warning=FALSE}
# select IVs
var <- select_vars(2)

# fit regression model
regress("collisions_overall")

# fit regression with interactions bw comms components and prop_female
interact_female("collisions_overall")

# interact_sex(vars$collisions_overall)

# alternative method of checking assumptions and multicollinearity
# library("olsrr")
# Vignette: https://cran.r-project.org/web/packages/olsrr/vignettes/regression_diagnostics.html
# VIFs > 4 require investigation
# Condition index: Collinearity is spotted by finding 2 or more variables that have large proportions of variance (.50 or more) that correspond to large condition indices. A rule of thumb is to label as large those condition indices in the range of 30 or larger.
# ols_coll_diag(fit)
# ols_correlations(fit) # Relative importance of independent variables in determining Y. How much each variable uniquely contributes to R2 over and above that which can be accounted for by the other predictors.
# ols_plot_diagnostics(fit)
# ols_plot_resid_regressor(fit)
```

## Speed overall
``` {r echo=FALSE, message=FALSE, warning=FALSE}
# select IVs
var <- select_vars(4)

# fit regression model
regress("speed_overall")

# fit regression with interactions bw comms components and prop_female
interact_female("speed_overall")

# interact_sex("collisions_overall")
# # with sex variable
# var2 <- select_vars_sex(4) %>% select(-leadership_co_driver, -sit.awareness_driver) # 19 drivers missing situation awareness data so removed
# 
# # mean center IVs
# var2_std <- var2 %>% 
#   mutate(sex_driver = factor(sex_driver)) %>%
#   mutate_if(is.numeric, scale, center=TRUE, scale=TRUE)
# 
# psych::describe(var2_std)
# 
# # regression without interactions
# fit2 <- lm(vars$speed_overall ~ .,
#            data = var2_std)
# 
# summary(fit2)
# ols_correlations(fit2)

# interact_sex("collisions_overall")

```

## Distance deviation overall
``` {r echo=FALSE, message=FALSE, warning=FALSE}
# select IVs
var <- select_vars(3)

# fit regression model
regress("distance_overall_deviation")

```

# No fog and fog events separately
``` {r echo=FALSE, message=FALSE, warning=FALSE}
x <- vars %>% 
  select(comms_fac, leadership:sit.awareness_driver,
         driving_years:neuroticism, effort:temporal_demand, driving_years_drone:neuroticism_drone, effort_drone, age_co_driver:prop_female,
         -contains("ratio"),
         collisions_fog_overall, collisions_no_fog_overall, speed_fog_overall, speed_no_fog_overall,
         distance_fog_overall, distance_no_fog_overall) %>% 
  correlate() %>% focus(collisions_fog_overall, collisions_no_fog_overall, speed_fog_overall, speed_no_fog_overall,
                        distance_fog_overall, distance_no_fog_overall) %>% 
  gather(var, val, -rowname) %>% 
  mutate(val = round(val, 2)) %>% 
  spread(var, val)

x[x > -.270 & x < .270] <- NA

name <- names(x)[-1]

lapply(name, function(i) {
  x <- x %>% select(rowname, i) %>% na.omit()
  kable(x)
})
```

## Regression models for each event (no fog/fog)
``` {r echo=FALSE, message=FALSE, warning=FALSE}
event_regression <- function(dv) {
  # print dv name
  print(paste0("DV = ", dv))
  
  # select variables
  a <- na.omit(x %>% select(rowname, dv)) %>% 
    # select(rowname) %>% 
    filter(!rowname %in% c("sex_driver", "sex_co_driver", "sit.awareness_driver", 
                           "sit.awareness_co_driver", "sit.awareness",
                           "leadership_driver", "leadership_co_driver", "leadership"))
  
  var <- vars %>% select(dv, a$rowname)
  n <- names(var[-1])
  
  # create regression formula
  fm <-   as.formula(paste(dv, " ~ ", paste(n, collapse = " + ")))
  
  # fit model
  f <- lm(fm, data = var)
  
  # results
  print(summary(f))
  
  # print(ols_correlations(f))
  
  # # check assumptions and multicollinearity
  # plot(f)
  # 
  # # plot correlations between IVs
  # p <- vars %>% select(n) %>% 
  #   ggcorr(method = "pairwise.complete.obs", 
  #          label = TRUE, label_size = 3, label_round = 2, label_alpha = TRUE, # add text correlations value to plot
  #          hjust = 0.9, size = 4, color = "grey50", layout.exp = 3) # move variable labels
  # # more detailed plot: distribution, scatterplot, correlations
  # # vars %>% select(x, issue) %>% 
  # #   ggpairs(., lower = list(continuous = wrap("smooth", alpha = 0.3, size=0.1)))
  # 
  # # print correlation plot
  # print(p)
  # 
  # # check for multicollinearity
  # print(omcdiag(vars %>% select(n), vars %>% select(dv)))
  # 
  # print(imcdiag(vars %>% select(n), vars %>% select(dv)))
  
}

# make list of event dv names
n <- c("collisions_no_fog_overall", "collisions_fog_overall", "speed_no_fog_overall",
"speed_fog_overall", "distance_no_fog_overall", "distance_fog_overall")

# fit regression model for each event DV
map(n, event_regression)

```