---
title: "EFA"
author: "Matt Blanchard"
date: "13/02/2020"
output: html_document
---
Used https://quantdev.ssri.psu.edu/tutorials/intro-basic-exploratory-factor-analysis as a guide to conduct EFA using R.

```{r setup, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

``` {r load, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(corrr)
library(broom)
library(lattice)
library(nFactors) # Determine Number of Factors to Extract
library(GPArotation)
library(corrplot)

# read in the data
d <- read_csv(here("data/200207_comms_vars.csv")) %>% 
  filter(team != "17080712_1") %>% 
  dplyr::select(co_info_help_overall:drive_frust_overall, 
                -contains("ratio"), -co_total_help_overall, 
                -co_total_harm_overall, -co_total_overall)
```

# Descriptive statistics
``` {r echo=FALSE, message=FALSE, warning=FALSE}
# d_std <- data.frame(scale(d, center=TRUE, scale=TRUE))
#descriptives
describe(d)

pairs.panels(d)
```

# Visualise correlations to see if variables cluster
``` {r echo=FALSE, message=FALSE, warning=FALSE}
corrplot(cor(d_std, use="complete.obs"), order = "hclust", tl.col='black', tl.cex=.75)
```

It looks like there are 3 clusters of positively correlated variables. 
1 Inform - Question + help/informs
2 Instruction
3 Negative


``` {r echo=FALSE, message=FALSE, warning=FALSE}
# create the correlation matrix for EFA so we know how it was done (e.g., how missing values were treated)
cor_d_std <- cor(d_std, use="pairwise.complete.obs")
cor_d_std
```

# How many factors to extract?
``` {r echo=FALSE, message=FALSE, warning=FALSE}
#parallel analysis for number of factors 
# fa.parallel(x = cor_d_std, fm = "ml", fa = "fa", n.obs = 55)

#multiple methods for number of factors
nScree(cor_d_std, model = "factors")
plot(nScree(cor_d_std, model = "factors"))

eigen(cor(cor_d_std))$values
```

Based on the scree plot it looks like there 3 factors.

# 3-factor EFA
``` {r echo=FALSE, message=FALSE, warning=FALSE}
# # prefer to run using correlation matrix but doesn't provide GFI
# efa_3factor <- fa(r = cor_d_std, nfactors = 3, 
#                        rotate = "varimax", 
#                        fm = "ml")

efa_3factor <- fa(r = d_std, nfactors = 3, 
                       rotate = "promax", 
                       fm = "paf",
                       scores="regression")



efa_3factor
```



# Predicted scores for 3 factors
Let's take a look at the reduced data
``` {r echo=FALSE, message=FALSE, warning=FALSE}
head(efa_3factor$scores, 10)

pairs.panels(efa_3factor$scores)
```

The 4 factors are not correlated with each other. Remember the variance accounted for by the 4 factors is only part of the total variance. Specifically, they account for `r round(100*efa_3factor$Vaccounted[3,4], 2)`% of the variance in the original 9 variables.



<!-- # CFA -->
<!-- ``` {r echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- library(lavaan) -->

<!-- # 3-factor model -->
<!-- instruct =~ co_instruct_help_overall + co_instruct_harm_overall + co_question_overall + drive_informs_overall -->
<!-- drive_info =~ co_info_help_overall + drive_question_overall -->
<!-- negative =~ co_info_harm_overall + co_redundant_overall + drive_frust_overall -->

<!-- # enter the model syntax -->
<!-- comms.model <- 'instruct =~ co_instruct_help_overall + co_instruct_harm_overall + co_question_overall + drive_informs_overall -->
<!-- drive_info =~ co_info_help_overall + drive_question_overall -->
<!-- negative =~ co_info_harm_overall + co_redundant_overall + drive_frust_overall' -->

<!-- # fit the model -->
<!-- fit_one <- cfa(comms.model, data=d_std, missing = "ML") -->

<!-- # display summary output -->
<!-- summary(fit_one, fit.measures=TRUE) -->

<!-- fitMeasures(fit_one, fit.measures= c("chisq", "df", "pvalue", "gfi", "tli",  -->
<!--                                  "cfi", "rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "aic")) -->


<!-- # 4-factor model -->
<!-- driver_info =~ co_info_help_overall + drive_question_overall + drive_informs_overall -->
<!-- instruct =~ co_instruct_help_overall + co_instruct_harm_overall -->
<!-- negative =~ co_info_harm_overall + co_instruct_harm_overall + co_redundant_overall + drive_frust_overall -->
<!-- co_info =~ co_question_overall + drive_informs_overall + co_instruct_harm_overall -->


<!-- # enter the model syntax -->
<!-- comms.model <- 'driver_info =~ co_info_help_overall + drive_question_overall -->
<!--                 instruct =~ co_instruct_help_overall + co_instruct_harm_overall -->
<!--                 negative =~ co_info_harm_overall + co_redundant_overall + drive_frust_overall -->
<!--                 co_info =~ co_question_overall + drive_informs_overall' -->

<!-- # fit the model -->
<!-- fit_one <- cfa(comms.model, data=d_std, missing = "ML") -->

<!-- # display summary output -->
<!-- summary(fit_one, fit.measures=TRUE) -->

<!-- fitMeasures(fit_one, fit.measures= c("chisq", "df", "pvalue", "gfi", "tli",  -->
<!--                                  "cfi", "rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "aic")) -->

<!-- # look at the correlation between the residuals -->
<!-- residuals(fit_one, type = "cor") -->

<!-- ``` -->
